Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2015-02-01 paper_linheng_4.tex
left related work and conclusion

Given a TM, the distance between a routing to the optimal one is defined as the ratio between their MLURs. Formally, a network is modeled as undirected graph $G(V, E)$, where $V$ is the set of vertices (nodes), and $E$ is the set of edges (links). Let $cap_{ij}$ denote the capacity of the link $(i, j) \in E$. Let $d_{ab}$ denote the traffic demand from origin node $a$ and destination node $b$, and $m$ denote the TM that contains $d_{ab}$ for all $a, b \in V$. Let $f_{ab}(i,j)$ be the fraction of $d_{ab}$ that is routed on link $(i, j)$ $(0 \leq f_{ab}(i,j) \leq 1)$. Routing $r$ is specified by $f_{ab}(i,j)$ for all $a, b \in V$ and $(i, j) \in E$, and we will formally define routing consistency later in Section III.C. Let $U_{r, m, G}$ be the MLUR of routing $r$ under TM $m$. We have
\begin{equation}
	U_{r, m, G} = \max_{(i,j)\in E} \frac{\sum_{a,b} d_{ab}f_{ab}(i,j)}{cap_{ij}}.
\end{equation}
Let $P(\{ r \},\{ m \}, G)$ be the \emph{performance ratio} of routing $r$ under TM $m$, which reflects how far from the routing to the optimal one, and is defined as
\begin{equation}
	P(\{ r \},\{ m \}, G) = \frac{U_{r,m,G}}{\min_{r'} U_{r', m, G}}.
\end{equation}

The \emph{oblivious performance ratio} (OPR) for routing $r$ is defined by extending TM $m$ to a set of TMs $M$, where $M$ can be the set of any TMs. We have
\begin{equation}
	P(\{ r \}, M, G) = \max_{m\in M} P(\{ r \}, \{ m \}, G).
\end{equation}
The target of demand-oblivious routing is to find routing $r$ that minimizes OPR $P(\{ r \}, M, G)$. Such a ``robust'' routing is independent of a specific TM, but can perform near optimally. A seminal work \cite{networking:oblivious} uses linear programming to find the routing that minimizes the OPR, and finds that the optimal solution exists, which means that the OPR is bounded.

@@

The intrinsic reason for such a ``fake robust'' is that the topology is not changing when performance ratio is computed in Eq. (2). To address this issue, we extend the definition of OPR. Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally give the model in Section III.C). The extended performance ratio is defined as
\begin{equation}
	P(\{ r \},\{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
\end{equation}
Let $P^*(\{ r \}, M, G)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$. We define $P^*(\{ r \}, M, G)$ by extending $m$ to $M$, and finding $G^*$ that satisfies the energy constraint and has the minimum performance ratio. We have
\begin{equation}
	P^*(\{ r \}, M, G) = \min_{G^*} \max_{m\in M} P(\{ r \}, \{ m \}, G, G^*)
\end{equation}
Note that when there is no energy constraint, $G$ is the sub-graph that has the minimum performance ratio, and Eq. (5) naturally reduces to Eq. (3).

\subsection{Problem Formulation}
We formulate our problem as following:

\begin{center}
Minimize \quad $P^*(\{r\},M,G)$
\end{center}

\begin{center}
s.t. (1),\ (4)
\end{center}

@@

\begin{equation}
    \begin{split}
    \sum_{j, s.t.(i,j) \in E}\hspace{-0.2in}f'_{ab}(i,j) - \hspace{-0.2in}\sum_{j, s.t.(j,i) \in E}\hspace{-0.2in}f'_{ab}(j,i) = 
    \left\{
        \begin{array}{c}
        \ \ 1, \ i = b \\
        -1, \ i = a \\
        \ \ \ \ \ 0, \ i \neq a,b \\
        \end{array}
    \right.
    \end{split}
\end{equation}

@@

\begin{equation}
    \begin{split}
    \sum_{j, s.t.(i,j) \in E^*}\hspace{-0.2in}f_{ab}(i,j) - \hspace{-0.3in}\sum_{j, s.t.(j,i) \in E^*}\hspace{-0.2in}f_{ab}(j,i) = 
    \left\{
        \begin{array}{c}
        \ \ 1, \ i = b \\
        -1, \ i = a \\
        \ \ \ \ \ 0, \ i \neq a,b \\
        \end{array}
    \right.
    \end{split}
\end{equation}

\begin{equation}
    \sum_{l \in E^*} p(l) / \sum_{l \in E} p(l) < 1 - \theta
\end{equation}

\begin{equation}
    0 \leq f_{ab}(i,j),f'_{ab}(i,j) \leq 1
\end{equation}

Eq. (6) is our target, which minimize the value of OPRE defined in \Rmnum{3}.B. Eq. (7) say $G^*$ be a sub-graph of $G$, which means remove/sleep
some links from $G$, and keep vertices the same. Eq. (8) ensures the graph is connected and define the routing. In details, $O_{(i,j)}^i$ equal to
1 if $i$ is the tail node of link $(i,j)$, and $I_(i,j)^i$ equal to 1 if $i$ is the head node of link $(i,j)$, this equation states the flow 
conservation constraints. In the other hand, $f_{ab}(i,j)$ is specified by routing $\gamma$, if the graph is not connected it will be unavailable
for some origin and destination pair. And from Eq. (8) we know that routing $r$ is corresponded with $G^*$, and $r'$ with $G$. We calculate the 
power constraints in Eq. (9), it ensure that we can save more than $\theta$ energy consumption. The function $p$ which maps link to power consumption
is proposed in \cite{networking:greente}.

\subsection{Model Example}
We will take an example to explain how to choose the link to close in our algorithm.
Three hostes include : a, b, c, three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose
there are two TM : ${(a,b,2M), (a,c,1M)}$ and ${(a,b,1M), (a,c,1M)}$. For each traffic matrix, the optimal route is
obvious, we will trace 2M from a to b across the lower link and trace the 1M from a to c across the upper one
for the first traffic matrix, whose maximum link utilization is 0.5. we will trace all the traffic acorss the
lower link for the second traffic matrix, whose maximum link utilization is 0.5 as well.

\begin{figure}[!t]
\centering
\vspace*{0.1in}
\includegraphics[width=8cm]{3-nodes-example}
\caption{Model Example, TM \Rmnum{1} : (a, b, 2M), (a, c, 1M); TM \Rmnum{2} : (a, b, 1M), (a, c, 1M).}
\label{label}
\vspace*{0.1in}
\end{figure}

Now for some reason, we will choose one link to shut down for power saving without lose connection of the network.
There are two choice, remove either the upper link or the lower link. Let us take a little calculation: when
remove the upper one, we should change all the traffic acorss the lower link, as a result, in the first
TM the maximum link utilization is 0.75 and the second is 0.5; when close the lower link, we should trace all the
traffic acorss the upper link, in the first TM the link utilization is 1 and the other is 0.667.
So according to our theory, the $P^{*}(M, G)$ should be 1.5 and the optimal successor network topology will be
the one which 3M link is closed.

\section{Algorithm}
In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
should be put to sleep from the origin topology based on extended robust link utilization (ERLU), 
then compute the robust routing based on demand-oblivious routing algorithm.

@@

\section{Samples and Proof}
For explaining OPRE clearly, we will show it in two simple topologies, Cliques and Cycles. With a specific power saving 
threshold, some links will be removed from the topology then robust routing will be computed. Taking two extreme examples from 
origin topology, one with no links removed, i.e the topology itself, and the other with no more link can be removed, i.e. 
spanning tree of the topology. And the corresponding thresholds are 0 and maximum value can be achieved. We prove the upper 
bound of OPRE for cycles and cliques in these two situations, and we say when taking a threshold between 0 and maximum value,
the corresponding OPRE is also bounded.

\begin{lemma}
The upper bound of OPR for $C_n$ (the cycle on n vertices) and $K_n$ (the complete graph on n vertices) is 2-2/n.
\end{lemma}

Lemma 1 is proved in \cite{networking:oblivious} and it assumes all the links the same. We extend this lemma on $C_n$ and
$K_n$ with different capacity of links. In the latter proof, we use the extended $C_n$ and $K_n$ definition without specified.

\begin{theorem}
The upper bound of OPRE for spanning tree of $C_n$ is 1+$Max_{cap}$/$Min_{cap}$.
\end{theorem}

\begin{proof}
Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 2.(a) show the six
nodes cycles topology, let nodes named from $A$ to $F$ and links named from $a$ to $f$. Now suppose a traffic in the 
topology then calculate the optimal routing for it, let $D_a$ and $C_a$ be the demand and capacity of the link $a$, 
without loss of generality, we say the link $d$ is the bottleneck, namely link with MLUR.

The spanning tree of $C_n$ is generated by removing one link from origin topology. There are two ways to generate 
the spanning tree, remove the link $d$ or remove the other link such as $f$.

For case \Rmnum{1}, when we switch off the link $d$, the origin traffic pass the link will be redirected. The worst situation
is that all the traffic on the link $d$ will be put to the other path : $D \leftarrow C \leftarrow B \leftarrow A \leftarrow 
F \leftarrow E$. After traffic redirection, the bottleneck link may become the link $e$, we have OPRE in this routing situation:

\begin{equation}
    \frac {\frac{D_e + D_d} {C_e}} {\frac {D_d}{C_d}} = (1 + \frac{D_e}{D_d}) \frac{C_d}{C_e}
\end{equation}

Because the link utilization of link $d$ is the maximum one, we have :

\begin{equation}
    \frac{D_d}{C_d} > \frac{D_e}{C_e} 
\end{equation}
\begin{equation}
    \frac{D_e * C_d}{C_e * D_d} < 1
\end{equation}

so we have OPRE in case \Rmnum{1} :

\begin{equation}
    (1 + \frac{D_e}{D_d}) \frac{C_d}{C_e} < \frac{C_d}{C_e} + 1
\end{equation}

For case \Rmnum{2}, similar to case \Rmnum{1}, all the traffic will be redirected on the other path between $F$ and $A$. There are two 
sub cases after traffic redirection, the link $D$ is still the bottleneck or the link $E$ become the new bottleneck. In case \Rmnum{2}.\Rmnum{1},
we have OPRE:

\begin{equation}
    \frac{\frac{D_d + D_f}{C_d}}{\frac{D_d}{C_d}} = 1 + \frac{D_f}{D_d}
\end{equation}

Because the link utilization of link $d$ is the maximum one in origin topology, we have:

\begin{equation}
    \frac{D_d}{C_d} > \frac{D_f}{C_f} 
\end{equation}
\begin{equation}
    \frac{D_f}{D_d} < \frac{C_d}{C_f} 
\end{equation}

So we get OPRE in case \Rmnum{2}.\Rmnum{1}:
\begin{equation}
    (1 + \frac{D_f}{D_d}) < \frac{C_d}{C_f} + 1
\end{equation}

In case \Rmnum{2}.\Rmnum{2}, we get OPRE:

\begin{equation}
    \frac{\frac{D_e + D_d}{C_e}}{\frac{D_d}{C_d}} = \frac{D_e * C_d}{D_d * C_e} * \frac{C_d * D_f}{C_e * D_e}
\end{equation}

Similarly as mentioned above, we get equations :

\begin{equation}
    \frac{D_d}{C_d} > \frac{D_e}{C_e} => \frac{D_e * C_d}{C_e * D_d} < 1 
\end{equation}
\begin{equation}
    \frac{D_d}{C_d} > \frac{D_f}{C_f} => \frac{D_f * C_d}{D_d} < C_f
\end{equation}

So we obtain OPRE:

\begin{equation}
    \frac{D_e * C_d}{D_d * C_e} + \frac{C_d * D_f}{C_e * D_d} < 1 + \frac{C_f}{C_e}
\end{equation}

As a result, the upper bound of extended robust link utilization must be :

\begin{equation}
    Max\{1 + \frac{C_d}{C_e}, 1 + \frac{C_d}{C_f}, 1 + \frac{C_f}{C_e}\} < 1 + \frac{Max_{cap}}{Min_{cap}}
\end{equation}

Particularly, if all the links have the same capacity, the upper bound equal to 2 for the spanning tree. Otherwise, the 
upper bound only dependent to the greatest ratio of link capacity.

\begin{theorem}
The upper bound of OPRE for $C_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
\end{theorem}

\begin{proof}
The robust routing which will not trace demand on one link must be less optimal than the routing can trace demand on any link,
and obviously the former routing is one of the routing on the spanning tree of $C_n$. So the bound of Theorem 2 is also the 
bound of Theorem 3.

Particularly, If the links of $C_n$ have the same capacity, OPRE will reduce to OPR. According to Lemma 1, we have the inequality:

\begin{equation}
OPRE = OPR < 2 - \frac{2}{n} < 1 + \frac{Max_{cap}}{Min_{cap}} = 2
\end{equation}

\begin{theorem}
The upper bound of OPRE for $K_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
\end{theorem}

\begin{proof}
Similar to the proof of Theorem 3, we say the robust routing which will not trace demand on one link must be less optimal than
the real optimal robust routing. And it is one routing of topology which remove one link from origin topology $K_n$. Without
loss of generality, we say the link $a$ is the bottleneck, and we will switch off it or other link like $b$, then consider
the OPRE when adjust the demand to other link.

In case \Rmnum{1}, after we switch off link $a$, the new bottleneck link must be the affected link, the link contains the origin 
traffic on link $a$. Otherwise if the link $b$ is the bottleneck, but we adjust the traffic on other links, it means that
we can do the same thing in the origin topology, and the bottleneck become link $b$ rather than $a$. It is conflict with our
assumption. So we have the OPRE as :

\begin{equation}
    \frac {\frac{D_b + D_a}{C_b}}{\frac{D_a}{C_a}} = (1+\frac{D_b}{D_a}) \frac{C_a}{C_b}
\end{equation}

Because the link $a$ is the bottleneck link with the maximum link utilization, like what we do above, we can get

\begin{equation}
    (1+\frac{D_b}{D_a}) \frac{C_a}{C_b} < 1 + \frac{C_a}{C_b}
\end{equation}

In case \Rmnum{2}, the bottleneck may still be link $a$ or the new link $c$. If it is link $a$, and no new traffic across it,
the OPRE equal to 1 obiliously. Or we adjust the new traffic $D_b$ on it, we can get the OPRE:

\begin{equation}
    \frac{\frac{D_a + D_b}{C_a}}{\frac{D_a}{C_a}} = 1 + \frac{D_b}{D_a} < 1 + \frac{C_b}{C_a}
\end{equation}

If the bottleneck become new link $c$, similar to our proof of circle topology, we can get OPRE:
\begin{equation}
    \frac{\frac{D_c + D_b}{C_c}}{\frac{D_a}{C_a}} = \frac{D_c * C_a}{D_a * C_c} + \frac{D_b * C_a}{D_a * C_c} < 1 + \frac{C_b}{C_c}
\end{equation}

So we obtain the same conclusion as circle topology, the OPRE must be :

\begin{equation}
    Max\{1 + \frac{C_a}{C_b}, 1 + \frac{C_b}{C_a}, 1 + \frac{C_b}{C_c}\} = 1 + \frac{Max_{cap}}{Min_{cap}}
\end{equation}

When the links of $K_n$ is the same, Theorem 4 will reduce to Lemma 1. The upper bound is bounded.
\end{proof}

\begin{theorem}
The upper bound of OPRE for spanning tree of $K_n$ is $\frac{n^2}{2} Max_{cap}/Min_{cap}$.
\end{theorem}

\begin{proof}
Every link in the spanning tree will split the graph to two parts, the flow between two parts must need across this link,
Without loss of generality, let $l_{da}$ be the link with maximum link utilization. And let $l_{be}$ be the bottleneck link 
in the optimal routing for origin topology. So we have OPRE:

\begin{equation}
    \frac{\frac{\sum_{i,j \in V} D_{ij}}{C_{da}}}{\frac{D_{be}}{C_{be}}} = \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} 
\end{equation}

Because the $l_{be}$ is the bottleneck link, we have:

\begin{equation}
    \frac{D_{ij}}{C_{ij}} < \frac{D_{be}}{C_{be}}
\end{equation}

\begin{equation}
    \frac{D_{ij}}{D_{be}} < \frac{C_{ij}}{C_{be}}
\end{equation}

\begin{equation}
    \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} < \sum_{i,j \in V} \frac{C_{ij}}{C_{be}}
\end{equation}

And we know that, the flow between two parts of topology must less than $\frac{n^2}{2}$, so OPRE must lower than:

\begin{equation}
    \sum_{i,j \in V} \frac{C_{ij}}{C_{be}} < \frac{n^2}{2} \frac{Max_{cap}}{Min_{cap}}
\end{equation}

@@

@@

>>>>

Given a TM, the distance between a routing to the optimal one is defined as the ratio between their MLURs. Formally, a network is modeled as undirected graph $G(V, E)$, where $V$ is the set of vertices (nodes), and $E$ is the set of edges (links). Let $cap_{ij}$ denote the capacity of the link $(i, j) \in E$. Let $d_{ab}$ denote the traffic demand from origin node $a$ and destination node $b$, and $m$ denote the TM that contains $d_{ab}$ for all $a, b \in V$. Let $f^r_{ab}(i,j)$ be the fraction of $d_{ab}$ that is routed on link $(i, j)$ $(0 \leq f^r_{ab}(i,j) \leq 1)$, using routing $r$. Routing $r$ is specified by $f^r_{ab}(i,j)$ for all $a, b \in V$ and $(i, j) \in E$, and we will formally define routing consistency later in Section III.C. Let $U_{r, m, G}$ be the MLUR of routing $r$ under TM $m$. We have
\begin{equation}
	U_{r, m, G} = \max_{(i,j)\in E} \frac{\sum_{a,b} d_{ab}f^r_{ab}(i,j)}{cap_{ij}}.
\end{equation}
Let $P(\{ r \},\{ m \}, G)$ be the \emph{performance ratio} of routing $r$ under TM $m$, which reflects how far from the routing to the optimal one, and is defined as
\begin{equation}
	P(r,\{ m \}, G) = \frac{U_{r,m,G}}{\min_{r'} U_{r', m, G}}.
\end{equation}

The \emph{oblivious performance ratio} (OPR) for routing $r$ is defined by extending TM $m$ to a set of TMs $M$, where $M$ can be the set of all TMs. We have
\begin{equation}
	P(r, M, G) = \max_{m\in M} P(r, \{ m \}, G).
\end{equation}
The target of demand-oblivious routing is to find routing $r$ that minimizes OPR $P(\{ r \}, M, G)$. Such a ``robust'' routing is independent of a specific TM, but can perform near optimally. A seminal work \cite{networking:oblivious} uses linear programming to find the routing that minimizes the OPR, and finds that the optimal solution exists, which means that the OPR is bounded.

@@

The intrinsic reason for such a ``fake robust'' is that the topology is not changing when performance ratio is computed in Eq. (2). To address this issue, we extend the definition of OPR. Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally define the energy constraint in Section III.C, i.e., Eq. (8)). Note that in this case, a path cannot traverse a off/sleeping link, so routing $r$ is limited by $G^*$ (Eq. (7) in Section III.C). The extended performance ratio is defined as
\begin{equation}
	P(r, \{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
\end{equation}
Let $P^*(r, M, G, G^*)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$. We define $P^*(r, M, G, G^*)$ by extending $m$ to $M$. Similar to Eq. (3), we have
\begin{equation}
	P^*(r, M, G, G^*) = \max_{m\in M} P(r, \{ m \}, G, G^*).
\end{equation}
Note that $G^*$ is used to achieve certain energy conservation target. For an energy conservation target, there may exist a set of different $G^*$, which result in different OPRE. We will show an example below. When there is no energy constraint, $G^*$ equals $G$, and Eq. (5) naturally reduces to Eq. (3).

\subsection{Example}

We show an example of our new metric OPRE. The network is shown in Fig. 1, where two nodes $a, b$ are connected by two links $l_1$ and $l_2$.{\footnote{When there are parallel links, we can add a virtual node in each parallel link to keep $G(V,E)$ as a simple graph.}} The capacities of the links are 3 Mbps and 4 Mbps, respectively. To forward a traffic demand of $d_{ab}$, the optimal routing is to put $\frac{3}{7}d_{ab}$ on link $l_1$ and $\frac{4}{7}d_{ab}$ on link $l_2$, which results in the MLUR of $\frac{1}{7}d_{ab}$. This routing is also the optimal demand-oblivious routing, because the routing is optimal no matter how $d_{ab}$ changes. Thus, the OPR equals 1.

\begin{figure}[!t]
\centering
\vspace*{0.1in}
\includegraphics[width=6cm]{3-nodes-example}
\caption{Model Example. There is traffic demand $d_{ab}$ from $a$ to $b$.}
\label{label}
\vspace*{0.1in}
\end{figure}

Now, assume that links $l_1$ and $l_2$ consume the same power, and one link has to be switched off/sleep to save energy. Let us check the OPRE after pruning $l_1$ and $l_2$, respectively. If $l_1$ is pruned, $d_{ab}$ is put on link $l_2$, and the MLUR is $\frac{1}{4}d_{ab}$, so the OPRE is $\frac{1}{4}d_{ab}/\frac{1}{7}d_{ab} = 7/4 = 1.75$. If $l_2$ is pruned, $d_{ab}$ traverses link $l_1$, resulting in the MLUR of $\frac{1}{3}d_{ab}$, so the OPRE is $\frac{1}{3}d_{ab}/\frac{1}{7}d_{ab} = 7/3 = 2.33$. The results tell us that pruning link $l_1$ is more robust than pruning link $l_2$. This is consistent with the intuition that link $l_2$ has a larger capacity and is stronger against congestion.

\subsection{Problem Formulation}

Now we formally model the problem. Our objective is to minimize OPRE $P^*(r, M, G, G^*)$, where $M$ and $G$ are inputs, and routing $r$ and sub-graph $G^*$ are decision variables. The Min-OPRE problem is as follows.

\begin{center}
Minimize \quad $P^*(r, M, G, G^*)$
\end{center}

\begin{center}
s.t. (1),\ (4),\ (5)
\end{center}

@@

\begin{equation}
    \begin{split}
    \sum_{j, s.t.(i,j) \in E}\hspace{-0.2in}f^{r'}_{ab}(i,j) - \hspace{-0.2in}\sum_{j, s.t.(j,i) \in E}\hspace{-0.2in}f^{r'}_{ab}(j,i) =
    \left\{
        \begin{array}{c}
        \ \ 1, \ i = a \\
        -1, \ i = b \\
        \ \ \ \ \ 0, \ i \neq a,b \\
        \end{array}
    \right.
    \end{split}
\end{equation}

@@

\begin{equation}
    \begin{split}
    \sum_{j, s.t.(i,j) \in E^*}\hspace{-0.2in}f^r_{ab}(i,j) - \hspace{-0.3in}\sum_{j, s.t.(j,i) \in E^*}\hspace{-0.2in}f^r_{ab}(j,i) =
    \left\{
        \begin{array}{c}
        \ \ 1, \ i = a \\
        -1, \ i = b \\
        \ \ \ \ \ 0, \ i \neq a,b \\
        \end{array}
    \right.
    \end{split}
\end{equation}

\begin{center}
    \vspace{0.1in}
    $\forall a,b \in V$, $\forall i,j \in E$: \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad 
    \vspace{-0.15in}
\end{center}

\begin{equation}
    0 \leq f^r_{ab}(i,j),f^{r'}_{ab}(i,j) \leq 1
\end{equation}

\begin{equation}
    \sum_{l \in E^*} p(l) / \sum_{l \in E} p(l) \leq 1 - \theta
\end{equation}

Constraints (1), (4), and (5) follow our definition of the OPRE. Eq. (6) means that the optimal routing $r'$ in $G$ must be a valid routing, i.e. with routing consistency. Specifically, for the source/destination node, all traffic must be routed/received; and for an intermediate node, the traffic flowing out must equal the traffic flowing in. Similarly, Eq. (7) means that the robust routing $r$ in $G^*$ must be a valid routing. Ineq. (8) means that the range of $f^r_{ab}(i,j)$ and $f^{r'}_{ab}(i,j)$ is from 0 to 1. Ineq. (9) means that the power consumption of links in $G^*$ must be less than a given threshold. In Ineq. (9), $\theta$ denotes the power saving ratio we must achieve by using $G^*$. Here, we use $p(l)$ to denote the power consumption of link $l$, which is mainly drawn by the line cards at the two ends of the link. Note that $p(l)$ is independent of the traffic volume, and this assumption is based on the fact that in current stage, the power of a line card changes little with the traffic volume \cite{networking:hopbyhop}.

Note that if $G^* = G$ satisfy the energy constraint Ineq. (9) and $M$ is the set of all TMs, the Min-OPRE problem reduces to the demand-oblivious routing problem, and can be transformed into a linear program and solved in polynomial time \cite{networking:oblivious}. However, we must find the optimal $G^*$ to achieve the required power saving ratio in other cases, and Min-OPRE is an MILP and is NP-hard in general.

Also note that we put the power saving in the constraint of our problem, instead of the objective function. In such a way, we can balance the trade off between energy conservation and the OPRE, by setting different values of power saving ratio $\theta$. We can even achieve the maximum power saving ratio by a binary search on $\theta$.

\section{Upper Bounds of the Minimum OPRE}

In this section, we analyze the upper bounds of the minimum OPRE. We are interested in two extreme types of networks, i.e., cycles and cliques, because general networks can be seen as intermediate cases between them. We will present the upper bounds with small and large values of $\theta$. We find that, though the minimum OPR of cycles and cliques is similar and bounded by 2 \cite{networking:oblivious}, the minimum OPRE is much more different and has a larger upper bound with a larger $\theta$. These theoretical results tell us that the robust energy efficient routing exists, and tell us how close a robust routing can get to the optimal routing.

\begin{lemma}
$\min P^*(r, M, G, G^*) \geq \min P^*(r, M, G)$ if $G^* \subseteq G$, where the equation holds if $G^* = G$.
\end{lemma}
\begin{proof}
We assume exist a $G^*$, s.t. min $P^*(r,M,G,G^*)$ $<$ min $P^*(r, M, G)$. Becuase $G^*$ is the subset of $G$, we directly
use the robust routing of $G^*$ to $G$, then $P^*(r, M, G)$ will equal to $P^*(r,M,G,G^*)$, and arise contradiction.
Particularly, when $G^* = G$, $G^*$ is the subset of $G$, and $G$ is the subset of $G^*$, so there is both 
min $P^*(r,M,G,G^*)$ $\geq$ min $P^*(r, M, G)$ and $P^*(r, M ,G)$ $\geq$ $P^*(r, M, G, G^*)$, so they are equal to each other 
when $G^*$ = $G$. This ends our proof.
\end{proof}

\begin{theorem}
The minimum OPRE of $C_n$ (the cycle on $n$ vertices with unit capacity links) and $K_n$ (the complete graph on $n$ vertices with unit capacity links) is $2-2/n$ if $\theta = 0$.
\end{theorem}
\begin{proof}
According to Lemma 1, the minimum OPRE of $C_n$ is the minimum OPR, i.e., $\min P^*(r, M, C_n)$, when $\theta = 0$. Similarly, the minimum OPRE of $K_n$ is $\min P^*(r, M, K_n)$ when $\theta = 0$. On the other hand, we know from \cite{networking:oblivious} that the minimum OPR of $C_n$ is $2-2/n$, and the minimum OPR of $K_n$ is also $2-2/n$. This ends our proof.
\end{proof}

Theorem 2 shows the minimum OPRE when $\theta = 0$ and all link capacities are the same. In a more general case when there are different link capacities, we have

\begin{theorem}
The upper bound of the minimum OPRE for a cycle on $n$ nodes is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$ if $\theta = 0$.
\end{theorem}
\begin{proof}
See Appendix A.
\end{proof}

\begin{theorem}
The upper bound of the minimum OPRE for a complete graph on $n$ nodes is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$ if $\theta = 0$.
\end{theorem}
\begin{proof}
See Appendix A.
\end{proof}

Theorem 3 and Theorem 4 tell us that the minimum OPRE is related to the link capacity difference in the network. The above results are for $\theta = 0$. Now let us see the results for a large $\theta$. Since there is not much difference between the power consumptions for links with different capacities \cite{}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$. We have
\begin{theorem}
Let $G^*$ be a spanning tree of a cycle on $n$ nodes, and then the upper bound of the OPRE is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$.
\end{theorem}
\begin{proof}
See Appendix B.
\end{proof}
\begin{theorem}
Let $G^*$ be a spanning tree of a complete graph on $n$ nodes, and then the upper bound of the OPRE is $\frac{n^2}{2} \frac{\max cap_{ij}}{\min cap_{ij}}$.
\end{theorem}
\begin{proof}
See Appendix C.
\end{proof}

Theorem 5 and Theorem 6 present a large gap between the OPRE upper bounds in the two types of networks, because when $G^*$ is a spanning tree, more links are pruned in the complete graph. This implies that in order to achieve more energy conservation, the OPRE may become larger quickly, and the routing becomes less robust, in the worst case. However, we can still develop effective algorithms to achieve a small OPRE and save energy in general cases, i.e., in real-world networks which have much less link densities than a complete graph.

\section{Robust Energy-Aware Routing Algorithms}

In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links
should be put to sleep from the origin topology based on extended robust link utilization (ERLU),
then compute the robust routing based on demand-oblivious routing algorithm.

@@

@@

\bibitem{networking:hopbyhop}
C. Hou, F. Zhang, A. F. Anta, L. Wang, and Z. Liu. “A Hopby-hop Energy Efficient Distributed Routing Scheme,” in Proc. of Greenmetrics Workshop, 2013.

@@

\appendices

\section{}
\begin{proof}
Fig. (5) shows the 6-nodes cycle and clique topologies. We label three links $l_{ab}$, $l_{cd}$ and $l_{ef}$
for our proof, let $cap_{ab}$, $cap_{cd}$ and $cap_{ef}$ be their link capacities. Now a arbitrary traffic
comes, we compute the optimal routing and forward the demand on the topologies, let $dem_{ab}$, $dem_{cd}$
and $dem_{ef}$ be the traffic on each link. Without loss of generality, we say the link $l_{ab}$ is the 
bottleneck, namely the link with MLUR.

Now let's consider the robust routing. When the routing changes, the traffic on each link also changes.
We image a simple situation, just forward the traffic from one link to another path base on the optimal
routing, and the link utilization of links on the path will increase, and accordingly the link 
utilization of former link will reduce to 0. Obviously, the routing must have a worse performance than 
the optimal robust routing, so its upper bound also is the bound of minimum OPRE.

For Case \Rmnum{1}.\Rmnum{1}, the adjusted link may be $l_{cd}$, the new bottleneck still be $l_{ab}$. 
The traffic on $l_{ab}$ is increased by the origin traffic on link $l_{cd}$, So we compute OPRE by:

\begin{equation}
\frac {\frac{dem_{ab} + dem_{cd}}{cap_{ab}}} {\frac{dem_{ab}}{cap_{ab}}} = 1 + \frac{dem_{cd}}{dem_{ab}}
\end{equation}

Because the old bottleneck is $l_{ab}$, so we have inequation:

\begin{equation}
\frac {dem_{cd}} {cap_{cd}} < \frac {dem_{ab}} {cap_{ab}}
\end{equation}

From Ineq. (14) we get:

\begin{equation}
\frac {dem_{cd}} {dem_{ab}} < \frac {cap_{cd}} {cap_{ab}}
\end{equation}

So we have OPRE in Case \Rmnum{1}.\Rmnum{1} combined by Eq. (13) and Ineq. (15):

\begin{equation}
1 + \frac {dem_{cd}} {dem_{ab}} < 1 + \frac {cap_{cd}} {cap_{ab}}
\end{equation}

For Case \Rmnum{1}.\Rmnum{2}, the adjusted link also be $l_{cd}$, but the new bottleneck may be $l_{ef}$.
Computing the OPRE similar as above:

\begin{equation}
\frac {\frac{dem_{ef} + dem_{cd}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} = 
\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac {dem_{cd} * cap_{ab}}{dem_{ab} * cap_{ef}}
\end{equation}

Because the old bottleneck is $l_{ab}$, so we have Ineq. (14) and :

\begin{equation}
\frac {dem_{ef}} {cap_{ef}} < \frac {dem_{ab}} {cap_{ab}}
\end{equation}

So we get inequation from Ineq. (18):

\begin{equation}
\frac {dem_{ef} * cap_{ab}} {dem_{ab} * cap_{ef}} < 1
\end{equation}

Also from Ineq. (14) we have :

\begin{equation}
\frac {dem_{cd} * cap_{ab}} {dem_{ab}} < cap_{cd}
\end{equation}

Combine Eq. (17), Ineq. (19) and Ineq. (20), we have OPRE in Case \Rmnum{1}.\Rmnum{2}:

\begin{equation}
\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac {dem_{cd} * cap_{ab}}{dem_{ab} * cap_{ef}} 
< 1 + \frac {cap_{cd}}{cap_{ef}}
\end{equation}

For Case \Rmnum{2}.\Rmnum{1}, the adjusted link may be $l_{ab}$, namely the old bottleneck link, the new bottleneck
maybe $l_{ef}$. Computing the OPRE similar as above:

\begin{equation}
\frac {\frac{dem_{ef} + dem_{ab}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} = 
\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac{cap_{ab}}{cap_{ef}} 
\end{equation}

Becuase the old bottleneck has the maximum link utilization, so combine Ineq. (19) and Eq.(22) we obtain OPRE in Case 
\Rmnum{2}.\Rmnum{1}:

\begin{equation}
\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac{cap_{ab}}{cap_{ef}} < 1 + \frac{cap_{ab}}{cap_{ef}}
\end{equation}

To sum up, we have inequation from Ineq. (16), Ineq. (21) and Ineq. (23):

\begin{equation}
1 + \max \{\frac{cap_{cd}}{cap_{ab}}, \frac{cap_{cd}}{cap_{ef}}, \frac{cap_{ab}}{cap_{ef}} \} < 1 + \frac{\max_{l \in E} cap_{l}}{\min_{l \in E} cap_{l}}
\end{equation}

\section{}
\begin{proof}
The spanning tree of circle is the topology which lose one link. In Appendix. A, when we consider the robust routing, we adjust the traffic 
on one link to another path, it is similar that we switch off the link and forward the traffic to some other path. The complete proof is 
almost the same with Appendix. A.
\end{proof}
